Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-13 MUSES_vs_BYOD_solutions.tex
Updating and changing all IBM subsection, closes #3

Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
more focused on the enterprise, offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords. Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs. On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side. Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art. The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.

@@

\subsection{IBM Hosted Mobile Device Security Management}
\label{subsec:ibm}

One of the first companies who supported the BYOD model was IBM in 2011 \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace. To help organizations \cite{ibm11} embracing both company and employee-owned mobile devices (as said, this practise is part of the BYOD model) in a security-rich environment, IBM developed a mobile device security management solution. For IBM, a mobile security strategy should focus on several key areas.

Thus, the organization should identify which business data the strategy will allow to be stored and processed on which mobile devices. This helps to determine what needs to be protected and to what degree. Then, since different mobile platforms have different native security mechanisms, the organization needs to define which mobile device platforms will be allowed in the business environment and, thus, which need to be supported in the mobile security strategy and plan. That means, to define the scope of the security plan. Also it is needed to decide the responsibility for mobile security management work, whether using the current IT security team to handle mobile devices, or outsourcing them to a managed security service provider. And no matter what the mobile environments are, a number of mobile ISPs and best-practise procedures need to be put in place and should also be identified in the company's mobile security strategic plan.

Taking into account these considerations, IBM developed a framework that specifies security domains and levels for applying various security technologies. When applied to mobile devices (not portable ones, so that laptops are not considered), the features of this framework depend on the deployment:

\begin{itemize}
	\item \textit{Identity and access}: Not only the use of strong passwords when accessing the devices, but also supply two way authentication and VPN access control, by supervising the authorised IP addresses and adding re-authentication for accessing resources (assets) with high value.
	\item \textit{Data protection}: Data security stored in the devices, related to professional life, is encrypted, also during the transmission. Moreover, when a device is lost, data can be removed remotely, and the device located or locked out (locking out a device is also made after a modifiable timeout). Finally, back ups are performed periodically once the device has been recovered.
	\item \textit{Application security}: This is related to the requirement of being connected from a controlled location for authorising the download of business applications, and those applications must be certified (also the currently running on the device). Actually, IBM's tool can monitor and remove applications which are identified as untrustworthy or unsafe.
	\item \textit{Fundamental integrity control}: Running both anti-malware software and personal firewall, and making the result of these tests as dependency for VPN's intranet access. 
	\item \textit{Governance and compliance}: Taking into consideration the mobile security as an important point in the overall risk management program of the company, and extend the periodic security audits to mobile devices too.
\end{itemize}

This solution is based on a client-server architecture, where the controlling center is placed in the server, and the client would be installed on the mobile devices. This way, the client/device would communicate with the server as regularly as possible, to enforce policies, execute commands, and report status. With these features, and by analysing in the server the incoming data from the devices, this IBM's solution would be able to help enterprises to support ISPs compliance and to recognise (consequently acting over) mobile threat landscapes.

%Regarding IBM hosted mobile device security solution's architecture, the solution is built on a sound client-server architecture in which the server centrally controls and manages security policies and settings for various security features. The client would be installed on the mobile device and regularly communicate with the server to enforce policies, execute commands and report status. Also, IBM's solution contains reporting and analysis capabilities, with information that helps the company to support ISP compliance, recognize the mobile threat landscape and evaluate the solution's effectiveness in countering threats.

>>>>

Many tools for companies, as well as for devices, which have adopted the BYOD have been released in the past four years. This way, and
more focused on the enterprise, there are some tools which offer the CSO ways to control the devices which enter in the system, requiring users to employ strong passwords, for instance, and also to protect the employees data by means of data encryption and data protection by having strong and secure passwords. Other tools for managing a BYOD situation add to their features guidelines for the CSOs to develop good ISPs. On the other hand, many solutions have been presented which are more focused on the device side, although they implement also the server side. Some of those tools have influenced the development of the MUSES system  itself (Section \ref{sec:muses}), which can complement them, as adds other features that go beyond the state of the art. The present section introduces the most relevant features of these products, as they can be considered related to the MUSES objectives.

@@

\subsection{IBM Mobile Security}
\label{subsec:ibm}

One of the first companies who supported the BYOD model was IBM \cite{IBM_tool}, as they recognized the increase of employees who brought their personal smartphones or tablets into the workplace \cite{ibm11}. IBM has different solutions divided into ``technology solutions'', and ``services'', and almost all are are mainly focused in the management of the devices in the system. Then, it might seem clear that the first disadvantage is not including all features in one system, but to make the companies to choose between one or another, or invest even more resources instead.

Having a look into what IBM offer as ``services'', three services can be found:

\begin{itemize} 
	\item \textit{Mobile Enterprise Services}: Is offered as an integrated solution for smartphones, and tablets as well, but then it is divided in different subservices that the company has to acquire separately. Some of them are related to cloud computing, such as events and log management as a cloud security service, cloud backup, or the so-called `hosted vulnerability management'. The last one is specially interesting for the scope of this paper, given the fact that it seems to implement one of the most important advantages of the MUSES system, the self-adaptation. IBM, by performing deeper scans over the security incidents data, either if they were successful (computer forensics analysis) or not (the device was enough secure), they claim to be able to recognise new vulnerabilities - or threats - with enough accuracy. The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately, and configuring the different parts.
	\item \textit{Hosted Mobile Device Security Management}: A particular service of the Mobile Enterprise Services. It includes itself a number of subservices, going from tools to make easy to develop secure mobile apps, to an interface for managing the devices in the system, check their configuration security level. Again, what is offered by IBM as `services', are included as default features in the MUSES system.
	\item \textit{Enterprise Wireless Networks}: Devoted to provide secure channels for communications. This is related with ensuring employees that any connection they might perform to access company assets, is properly secured, at the time it delivers the expected performance. Thus, this service is, in some sense, adaptive to the situation, yet only in terms of a secure connection and not evolvind the security policies, like MUSES. 
\end{itemize}
